---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# autoscore

The goal of autoscore is to score the accuracy of speech perception (often in several situations such as noise, dysarthria, hearing loss, etc.). It uses a flexible number of rules that help decide if a response set of words match a target set of words. Each rule can be applied or removed in each situation to best meet the needs of the reseearcher.

The rules are:

1. `position_rule` = how close the word has to be in the order of the target (e.g., `c("one", "two") with c("three", "one", "two")` has "one" match one position off of where it should be and same with "two")
2. `homophone_rule` = should we use homophone list (`TRUE` or `FALSE`)
3. `stemmed_rule` = should we stem all words (i.e., remove all suffixes); default is `TRUE`
3. `pasttense_rule` = -d and -ed removed (is not applied when `stemmed_rule` is applied); default is `TRUE`
4. `a_the_rule` = a and the are the same
5. `plural_rule` = remove plurals (is not applied when `stemmed_rule` is applied); default is `TRUE`
6. `firstpart_rule` = embedded at beginning of word or at the end of the word ("bat" :: "batman"); uses a partial matching heuristic
7. `alternate_spell_rule` = user provided alternate spellings of words in the target

## Design

The API of the `R` package is simple. A single call to `autoscore()` with the formatted data will run everything for you. This function is a composite of several sub-functions that do various jobs:

- `select_cols()` -- The first function which takes the data and gets it in the right format for analysis.
- `split_clean()` -- Using the cleaned data from `select_cols()`, this uses `stringr` to turn the phrases into individual words.
- `homophones_fun()` -- If homophones are used (according to the `homophone_rule`), this function finds and normalizes all homophones as found in the `data(homophones)` found in this package.
- `match_position_basic()` -- This function is the workhorse of the package. It takes the cleaned (and possibly homophone normalized) data and does three main things: 1) applies all the rules except for the `position_rule`, 2) finds the matches between the responses and the targets, and 3) reports how far away the matches are from each other.
- `count_matches()` -- Finally, this function takes the information from `match_position_basic()` and counts the number of matches based on the `position_rule`.


## Use of the Online Tool

The online tool will be developed shortly...




## Use of the R Package

An example of the use of `autoscore` is below. We will use the example data set provided in the package.

```{r}
library(tidyverse)
library(autoscore)

data("example_data")
example_data
```

First, let's use all the defaults and look at the first 10 rows of the output.
```{r}
example_data %>%
  autoscore() %>%   ## using all the defaults
  as.tibble()       ## to shorted output
```

Next, let's change some of the rules.
```{r}
example_data %>%
  autoscore(position_rule = 2, stemmed_rule = FALSE) %>%
  as.tibble()
```

We can also change the output type to "none" to get all the data from the computation.
```{r}
example_data %>%
  autoscore(output = "none")
```

In each of these exapmles, it is clear that the human and "robot" agree the majority of the time. The times that they disagree, it is usually predictably a human error or a subjective judgement that the researcher will have to consider (for example by including alternate spellings of words; see `alternate_spell_rule`).

Finally, the session information from the computer that ran this short tutorial.
```{r}
devtools::session_info("autoscore")
```


